Appendix 4: Species distribution model comparison between INLA and sdmTMB

### 2022-01-05 doc/appendix-binomial-inla.Rmd
Update appendix-binomial-inla.Rmd

# INLA

Data preparation for INLA models includes a formula, as well as objects made using several different functions including: `inla.spde.make.index()`, `inla.spde.make.A()`, and `inla.stack()`.
We use `control.inla = list(int.strategy = "eb", strategy = "gaussian")` for comparability with TMB (REF).
We use weak priors on the fixed effects (`mean = 0, prec = 1/(100*100)`), which amounts to a `Normal(0, 100^2)` prior.

>>>>

# INLA 
<-- EW: missing a citation in REF below -->
Data preparation for INLA models includes a formula, as well as objects made using several different functions including: `inla.spde.make.index()`, `inla.spde.make.A()`, and `inla.stack()`.
We use `control.inla = list(int.strategy = "eb", strategy = "gaussian")` for comparability with TMB (REF).
We use weak priors on the fixed effects (`mean = 0, prec = 1/(100*100)`), which amounts to a `Normal(0, 100^2)` prior.
